Applied Measure Theory for Probabilistic Modeling

### 2022-05-13 paper/paper.tex
edits

 This is a very relevant question for probabilistic programming tasks and causal inference, and with \emph{kernels} \verb|MeasureTheory| does provide tools to reason about it which are computationally appropriate, because they are local.

@@

We'll now discuss the mechanics of defining a measure, followed by {\bf XXX description of the next subsection XXX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kernels}

>>>>

 This is a very relevant question for probabilistic programming tasks and causal inference, and with \emph{kernels} (Section~\ref{Kernels}) \verb|MeasureTheory| does provide tools to reason about it which are computationally appropriate, because they are local.

\chad{above paragraph needs editing}

@@

We'll now discuss the mechanics of defining a measure, followed by 
\chad{add a description of the next subseciton here}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kernels\label{Kernels}}
